# In-Class Programming Activity, Day 9

Delia Walker-Jones

Create deck:
```{r}
poker_deck <- c(outer((10 * 2:14), 1:4, '+'))
```

Calculating suits and ranks
```{r}
test_hand <- sample(poker_deck, 5)

suits <- function(deck){
  deck[1:length(deck)] %% 10
}

ranks <- function(deck){
  deck[1:length(deck)] %/% 10
}
```

### Function 1
Royal flush: <0.001% five cards of the same suit with ranks 10, ack, queen, king, ace. This could also be called a royal straight flush, but a royal flush is by necessity a straight flush.
```{r}
is_royal_flush <- function(){
  
}
```

### Function 2
Straight flush (not including royal flush): <0.002% five cards of the same suit in consecutive order
```{r}
is_straight_flush <- function(five_cards){
  suit_count <- table(suits(five_cards))
  consecutive <- diff(sort(ranks(five_cards)))
  if (max(suit_count) == 5 && max(consecutive == 1)) {
    check <- TRUE
  }
  else {
    check <- FALSE
  }
  check
}

straight_flush_test <- c(21, 31, 41, 51, 61)
is_straight_flush(straight_flush_test)
is_straight_flush(test_hand)
```

### Function 3
Four of a kind 0.02% four cards of the same value (and, necessarily, different suits)
```{r}
is_four_of_a_kind <- function(five_cards){
  rank_count <- table(ranks(five_cards))
  if (max(rank_count) == 4) {
    check <- TRUE
  }
  else {
    check <- FALSE
  }
  check
}

four_of_a_kind_test <- c(44, 41, 42, 43, 104)
is_four_of_a_kind(four_of_a_kind_test)
is_four_of_a_kind(test_hand)
```

### Function 4
Full house: 0.14% Three of a kind and the other two cards forming a pair
```{r}
is_full_house <- function(five_cards){
  counts <- table(ranks(five_cards))
  if (min(counts) == 2 && max(counts) == 3) {
    check <- TRUE
  }
  else {
    check <- FALSE
  }
  check
}
test_hand
is_full_house(test_hand)
```

### Function 5
Flush (excluding royal flush and straight flush): 0.20%
five cards of the same suit
```{r}
is_flush <- function(five_cards){
  suit_count <- table(suits(five_cards))
  if (max(suit_count) == 5) {
    check <- TRUE
  }
  else {
    check <- FALSE
  }
  check
}
```

### Function 6
Straight (excluding royal flush and straight flush): 0.39%
five consecutively numbered cards
```{r}
is_straight <- function(five_cards){
  consecutive <- diff(sort(ranks(five_cards)))
  if (max(consecutive) == 1) {
    check <- TRUE
  }
  else {
    check <- FALSE
  }
  check
}

is_straight(c(21, 31, 42, 52, 62))
```

### Function 7
```{r}
is_three_of_a_kind <- function(five_cards){
  suit_count <- table(suits(five_cards))
  if (max(suit_count) == 3) {
    check <- TRUE
  }
  else {
    check <- FALSE
  }
  check
}
```

### Function 8
```{r}
is_two_pair <- function(five_cards){
  suit_count <- table(suits(five_cards))
  if (max(suit_count) == 2) {
    check <- TRUE
  }
  else {
    check <- FALSE
  }
  check
  
}
```

### Function 9
```{r}
is_pair <- function(five_cards){
  suit_count <- table(suits(five_cards))
  if (max(suit_count) == 2) {
    check <- TRUE
  }
  else {
    check <- FALSE
  }
  check
}
```













## Test statements

```{r}
scoreActivity::score253(9)
```