# Abstract for the End-of-Term Project

You'll give a description of your project here, including the names of all of your group members.
```{r, cache = TRUE}
library(dplyr)
library(ggplot2)
library(MASS)
h1b = read.csv("h1b_kaggle.csv")
names(h1b)

h1bsubset <- na.omit(subset(h1b, CASE_STATUS=='CERTIFIED' | CASE_STATUS == 'CERTIFIED-WITHDRAWN'))

h1bsubset[,9] = toupper(h1bsubset[,9])
h1bsubset[,4] = toupper(h1bsubset[,4])
#sort(table(h1bsubset$WORKSITE), decreasing = TRUE)
#sort(table(h1bsubset$EMPLOYER_NAME), decreasing = TRUE)
#sort(table(h1bsubset$SOC_NAME), decreasing = TRUE)
dim(h1bsubset)
table(h1bsubset$CASE_STATUS)
```

```{r}

worksiteTab <- table(h1bsubset$WORKSITE)
h1bsubsetA <- droplevels(h1bsubset[h1bsubset$WORKSITE %in% names(worksiteTab)[worksiteTab >= 1000],,drop=FALSE])
#dim(h1bsubsetA)
#min(table(h1bsubsetA$WORKSITE))
#sort(table(h1bsubsetA$WORKSITE), decreasing = TRUE)
#sort(table(h1bsubsetA$SOC_NAME), decreasing = TRUE)

socTab = table(h1bsubsetA$SOC_NAME)
h1bsubsetB <- droplevels(h1bsubsetA[h1bsubsetA$SOC_NAME %in% names(socTab)[socTab >= 10000],,drop=FALSE])
dim(h1bsubsetB)
min(table(h1bsubsetB$SOC_NAME))
sort(table(h1bsubsetB$SOC_NAME), decreasing = TRUE)

#ggplot(h1bsubsetB, aes(x = CASE_STATUS, y = PREVAILING_WAGE)) + geom_bar(stat = "identity")

#x <- factor(x)
#levels(x) <- list(Yes=c("Y", "Yes"), No=c("N", "No"))

socnameList <- factor(h1bsubsetB$SOC_NAME)
levels(socnameList) <- list(COMPUTER_DEVELOPMENT=c("SOFTWARE DEVELOPERS, APPLICATIONS", "COMPUTER PROGRAMMERS", "COMPUTER OCCUPATIONS, ALL OTHER"), COMPUTER_SYSTEMS=c("COMPUTER SYSTEMS ANALYSTS", "SOFTWARE DEVELOPERS, SYSTEMS SOFTWARE", "NETWORK AND COMPUTER SYSTEMS ADMINISTRATORS", "DATABASE ADMINISTRATORS", "COMPUTER SYSTEMS ANALYST"), ENGINEERS=c("ELECTRONICS ENGINEERS, EXCEPT COMPUTER", "MECHANICAL ENGINEERS"), MANAGERS=c("MANAGEMENT ANALYSTS", "COMPUTER AND INFORMATION SYSTEMS MANAGERS"), OTHER_FINANCE=c("ACCOUNTANTS AND AUDITORS", "FINANCIAL ANALYSTS", "MARKET RESEARCH ANALYSTS AND MARKETING SPECIALISTS", "OPERATIONS RESEARCH ANALYSTS"))

#socnameList

h1bsubsetB$SOC_GROUP = socnameList

summary(h1bsubsetB$SOC_GROUP)

dim(h1bsubsetB)

write.csv(h1bsubsetB, file = "h1bsubset.csv")

```
COMPUTERDEVELOPMENT:SOFTWARE DEVELOPERS, APPLICATIONS, COMPUTER PROGRAMMERS, COMPUTER OCCUPATIONS, ALL OTHER

COMPUTER SYSTEMS: COMPUTER SYSTEMS ANALYSTS, SOFTWARE DEVELOPERS, SYSTEMS SOFTWARE, NETWORK AND COMPUTER SYSTEMS ADMINISTRATORS, DATABASE ADMINISTRATORS, COMPUTER SYSTEMS ANALYST

ENGINEERS: ELECTRONICS ENGINEERS, EXCEPT COMPUTER, MECHANICAL ENGINEERS

MANAGERS: MANAGEMENT ANALYSTS, COMPUTER AND INFORMATION SYSTEMS MANAGERS

OTHER (FINANCE, ETC): ACCOUNTANTS AND AUDITORS, FINANCIAL ANALYSTS, MARKET RESEARCH ANALYSTS AND MARKETING SPECIALISTS

```{r}
library(MASS)
h1b = read.csv("h1bsubset.csv")

h1bdata = subset(h1b, X != 803878 | X != 1010468)

set.seed(1)
train = sample(c(TRUE, FALSE), nrow(h1bdata), rep = TRUE)
test = (!train)
CASE_STATUStest = h1bdata[test,]$CASE_STATUS
head(CASE_STATUStest)

lda.Mod = lda(CASE_STATUS ~ SOC_GROUP + PREVAILING_WAGE +FULL_TIME_POSITION + YEAR, data = h1bdata, subset = train)
lda.Mod

xnames = dimnames(coef(lda.Mod))[[1]]
plot(lda.Mod, xlab = xnames)
```
```{r}
lda.Pred = predict(lda.Mod, h1bdata[test,])
names(lda.Pred)
lda.Class = lda.Pred$class
table(lda.Class, h1bdata[test,]$CASE_STATUS)

mean(lda.Class==h1bdata[test,]$CASE_STATUS)
```



Also, give a link to the public GitHub repository you and your team created to hold your work.


```{r}
library(rpart)
tree1 = rpart(CASE_STATUS ~ SOC_GROUP + PREVAILING_WAGE +FULL_TIME_POSITION + YEAR, data = h1bdata, subset = train, cp = 0.001)

```